---
title: "Appendix"
author: "Margaret Perry, Rutendo Madziwo, Zainab Rizvi"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(mosaic)
library(ggplot2)
require(magrittr)
require(tidyverse)
require(leaps)
require(agricolae)
require(Stat2Data)
require(leaps)
library(leaps)
require(stargazer)
library(car)
require(car)
library("ggthemes")
library("scales")
collegedata <- read_csv("data.csv")
collegeChardata <- read_csv("data2.csv")
newData = inner_join(collegeChardata, collegedata, by="name")
newData = newData %>%
  mutate(sqrtalien_share_fall_2000 = sqrt(alien_share_fall_2000))
newData = newData %>%
  mutate(mobility = kq5_cond_parq1)
Lm1<-lm(mobility~endowment_pc_2000+par_median+pct_stem_2000+sqrtalien_share_fall_2000+black_share_fall_2000+tier +par_median*tier, data= newData)

```


## Figure A: Results of model selection using all subsets 

```{r echo=FALSE}
allsubsets<-regsubsets(mobility~ count + endowment_pc_2000+par_median+pct_stem_2000+sqrtalien_share_fall_2000+ black_share_fall_2000 +hbcu+ tier, data= newData)
plot(allsubsets, scale= "adjr2")
```

## Figure B: Residual plots that confirm that conditions of inference are met

```{r echo=FALSE}
plot(residuals(Lm1))
abline(0,0)
plot(Lm1)
```

## Figure C: Summary of the regression model

```{r echo=FALSE}
stargazer(Lm1, type="text")
```

## Figure D: Tier vs Mobility plot

```{r echo=FALSE}
plot(mobility ~ tier, data=newData)
```

## List of tiers: 

1. Ivy Plus 

2. Other elite schools (public and private) 

3. Highly selective public 

4. Highly selective private 

5. Selective public 

6. Selective private 

7. Nonselective 4-year public 

8. Nonselective 4-year private not-for-profit 

9. Two-year (public and private not-for-profit) 

10. Four-year for-profit 

11. Two-year for-profit 

12. Less than two year schools of any type


