---
title: "Draft Project"
date: "11/7/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(readr)
library(mosaic)
library(ggplot2)
require(magrittr)
require(tidyverse)
require(leaps)
require(Stat2Data)
require(leaps)
library(leaps)
library(car)
require(car)
collegedata <- read_csv("data.csv")
collegeChardata <- read_csv("data2.csv")
```

## Joining the two tables on the name of the college
```{r}
newData = inner_join(collegeChardata, collegedata, by="name")
```

## Transforming the alien share explanatory variable
```{r}

# before transformation
c <- ggplot(newData, aes(alien_share_fall_2000))
c+geom_histogram()

newData = newData %>%
  mutate(sqrtalien_share_fall_2000 = sqrt(alien_share_fall_2000))

# after transformation
d <- ggplot(newData, aes(sqrtalien_share_fall_2000))
d+geom_histogram()

```


# Running stepwise regression

```{r}
#just to remove missing values of variables 
newData = newData%>%
  filter(!is.na(tier),!is.na(hbcu),!is.na(black_share_fall_2000),!is.na(sqrtalien_share_fall_2000),!is.na(pct_stem_2000),
         !is.na(par_median),!is.na(endowment_pc_2000),!is.na(count),!is.na(kq5_cond_parq1))

nullmodel <- lm(kq5_cond_parq1~1, data = newData)
fullmodel <- lm(kq5_cond_parq1~tier + hbcu + black_share_fall_2000 + sqrtalien_share_fall_2000 + pct_stem_2000 + par_median + endowment_pc_2000 + count, data = newData)

# With 'scale=fullMSE', the AIC term can be interpreted as Cp
fullMSE <- (summary(fullmodel)$sigma)^2

step(nullmodel, scope = list(upper = fullmodel),
scale = fullMSE, direction = "both")
```

## All subsets approach

```{r}
allsubsets<-regsubsets(kq5_cond_parq1~ count + endowment_pc_2000+par_median+pct_stem_2000+sqrtalien_share_fall_2000+ black_share_fall_2000 +hbcu+ tier, data= newData)
plot(allsubsets, scale= "adjr2")
```


Both gave us the same model!

## We will also look at the correlation matrix to see if some variables are collinear

```{r}
newData %>%
  select(c(sqrtalien_share_fall_2000,endowment_pc_2000, par_median, tier, black_share_fall_2000, pct_stem_2000))%>%
  cor()
```

Nothing is collinear!

## Now lets fit this model

```{r}
Lm1<-lm(kq5_cond_parq1~endowment_pc_2000+par_median+pct_stem_2000+sqrtalien_share_fall_2000+black_share_fall_2000+tier, data= newData)
summary(Lm1)
```

## Variance Inflaction Factor

```{r}
vif(Lm1)
```

Everything looks good! Other *exploratory* analysis suggested that we may have some collinearity between par_median and tier so we will add an interaction term to explain this.

# Model including the interaction term

```{r}
m1<-plot(kq5_cond_parq1~endowment_pc_2000+par_median+pct_stem_2000+sqrtalien_share_fall_2000+black_share_fall_2000+tier +par_median*tier, data= newData)

Lm1<-lm(kq5_cond_parq1~endowment_pc_2000+par_median+pct_stem_2000+sqrtalien_share_fall_2000+black_share_fall_2000+tier +par_median*tier, data= newData)

summary(Lm1)
```

It explains 68% of the variability in the response. 

## Nested F- tests

# Nested F-test to check endowment
```{r}
Lm1<-lm(kq5_cond_parq1~endowment_pc_2000+par_median+pct_stem_2000+sqrtalien_share_fall_2000+black_share_fall_2000+tier +par_median*tier, data= newData)

nested1 <- lm(kq5_cond_parq1~par_median+pct_stem_2000+sqrtalien_share_fall_2000+black_share_fall_2000+ tier +par_median*tier, data= newData)
anova(nested1, Lm1)
```

The nested model does not have endowment. Since the p-value < 0.05 we should use the full model and keep endowment.

# Nested F-test to check par_median 
```{r}
Lm<-lm(kq5_cond_parq1~endowment_pc_2000+par_median+pct_stem_2000+sqrtalien_share_fall_2000+black_share_fall_2000+tier +par_median*tier, data= newData)

nested2 <- lm(kq5_cond_parq1~endowment_pc_2000 + pct_stem_2000+sqrtalien_share_fall_2000+ black_share_fall_2000 + tier, data= newData)
anova(nested2, Lm)
```

The nested model does not have par_median Since the p-value < 0.05 we should use the full model and keep par_median.

# Nested F-test to check tier 

```{r}
Lm<-lm(kq5_cond_parq1~endowment_pc_2000+par_median+pct_stem_2000+sqrtalien_share_fall_2000+black_share_fall_2000+tier +par_median*tier, data= newData)

nested2 <- lm(kq5_cond_parq1~ endowment_pc_2000 + pct_stem_2000+sqrtalien_share_fall_2000+ black_share_fall_2000 + par_median, data= newData)
anova(nested2, Lm)
```
The nested model does not have tier Since the p-value < 0.05 we should use the full model and keep tier

## Analysis of residuals

```{r}
plot(residuals(Lm1))
abline(0,0)
plot(Lm1)
```
```{r}
summary(Lm1)
```


After having checked the importance of our variable, our fitted model is 

$\widehat{kq5\_cond\_parq1} = -11.18 - 0.00002229endowment\_pc\_2000 + 0.0004459par\_median + 0.2167pct\_stem\_2000 +  25.84sqrtalien\_share\_fall\_2000 - 3.361black\_share\_fall\_2000 + 1.494tier + 0.0000405par\_median\cdot tier$

68% of the variability in the percentage of children who reach the Top 20% of the income distribution among children with parents in the bottom 20% of the income distribution (kq5_cond_parq1) is explained by the model. 

According to the model:
\begin{description}
   \item[$\bullet$] When there are no variables, the kq5_cond_parq1 decreases by 11.18%, 
   \item[$\bullet$] Holding all else constant, a $1 increase in endowment results in a 0.00002229% decrease in kq5_cond_parq1,
   \item[$\bullet$] Holding all else constant, a $1 increase in parents' median income results in a 0.0004459% increase in kq5_cond_parq1,
   \item[$\bullet$] Holding all else constant, a percentage increase in stem students results in a 0.2167% increase in kq5_cond_parq1,
   \item[$\bullet$] Holding all else constant, if we add one more foreign student, we increase the percentage of kq5_cond_parq1 by 25.84%,
   \item[$\bullet$] Holding all else constant, if we add one more black student, kq5_cond_parq1 decreases by 3.361%,
   \item[$\bullet$] Holding all else constant, a one unit increase in tier increases the kq5_cond_parq1 by 1.494%. We will need to make this variable a factor. 
   \item[$\bullet$]Holding all else constant, a $1 increase in parents median results in a 0.0000405% increase in kq5_cond_parq1 while moderating for tier. 
\end{description}





